Spatial Analysis

### 2021-04-26 Scripts/spatial_analisis.Rmd
exploring border extrapolation

us_map <- st_as_sf(map("state", plot = FALSE, fill = TRUE))

@@

>>>>

us_map <- st_as_sf(map("state", plot = FALSE, fill = TRUE)) %>% 
  filter(ID %in% c("maine", "new hampshire", "massachusets", "connecticut", "rhode island", "new york", "new jersey", "delaware", "maryland", "virginia", "north carolina"))

@@

# US state waters
# https://www.fisheries.noaa.gov/inport/item/39963

path_world <- MyFunctions::my_path("D", extra_path = "Spatial/USMaritimeLimitsAndBoundariesSHP")
path_world <- "~/Desktop/GAFBorders"

# The File
fnam_world <- "Statistical_Areas_2010_withNames.shp"

# Load it!
us_sf <- st_read(dsn = path_world,
                        layer =file_path_sans_ext(fnam_world)) %>% 
  st_transform(crs = 4326) %>% # 4326
  janitor::clean_names() %>% 
  # st_transform(crs = "+proj=eck4") %>% # for tbular plot
  st_simplify(preserveTopology = TRUE, dTolerance = 0.1) #%>% 
  # filter(region == "Atlantic Coast and Gulf of Mexico")
  # filter(name %in% c("Maine", "Vermont", "New Hampshire", "Massachusets", "Connecticut", "rhode island", "new york", "new jersey", "delaware", "maryland", "virginia", "north carolina", "south carolina", "georgia", "florida", "pennsylvania"))

us_sf$full_name

ggplot(us_sf) +
  geom_sf(aes(fill = nafodiv)) +
  geom_sf(data =  us_map,aes()) +
  coord_sf(xlim = c(-76, -65),ylim = c(35, 45))

us_map %>% 
  ggplot() +
  geom_sf(aes(fill = ID)) +
  # geom_sf(data =  us_map,aes()) +
  coord_sf(xlim = c(-76, -65),ylim = c(35, 45))

st_intersects(us_map)

### Exploring spatial regions

```{r}
